Model LF

### 2022-09-29 Estimation.Rmd
lavet komp_r uden seasonality og ændret behavioral equations

@@

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),1:4) +  L(TSDELTALOG(komp_r_obs),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part1),1) + L(log(komp_r_obs),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs), 0:4)", c(1,2,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part1), 1:4)", c(1,3))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,1,2,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),c(2,4)) +  L(TSDELTALOG(komp_r_obs),c(0,3))+  L(TSDELTALOG(rw_ds),0:1) + L(TSDELTA(ur_ds),3)+ L(log(part1),1) + L(log(komp_r_obs),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

@@

```{r}
reg_kuld_start=dynlm(TSDELTALOG(kuld_2017) ~ 1 + L(TSDELTALOG(kuld_2017),1:4) +  L(TSDELTALOG(komp_r_obs_2017),0:4)+ L(log(kuld_2017),1) + L(log(komp_r_obs),1)+ d_2013q1+ d_2009q1)

@@

@@

 kuld_vars_1 <- str_c("L(TSDELTALOG(kuld_2017), 1:4)", c(1,2,3,4))
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs_2017), 0:4)", c(1,2,3))

@@

```{r}
reg_kuld=dynlm(TSDELTALOG(kuld_2017) ~ 0  +  L(TSDELTALOG(komp_r_obs_2017),c(0,4))+ L(log(kuld_2017),1) + L(log(komp_r_obs),1)+ d_2013q1+ d_2009q1)

summary(reg_kuld)
```

>>>>

d_2015q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2015,1), dummy_end = c(2015,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2014q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2014,1), dummy_end = c(2014,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2016q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2016,1), dummy_end = c(2016,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

komp_r_obs1=mean_dp_regul/wage_ds

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),1:4) +  L(TSDELTALOG(komp_r_obs1),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part1),1) + L(log(komp_r_obs1),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs1), 0:4)", c(1,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part1), 1:4)", c(1,3,4))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(0,2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,1,2,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),c(2)) +  L(TSDELTALOG(komp_r_obs1),c(0,2,3))+  L(TSDELTALOG(rw_ds),1) + L(log(part1),1) + L(log(komp_r_obs1),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
kuld_2017= window(kuld, end= c(2017,4), frequency= 4)
komp_r_obs1_2017= window(komp_r_obs1, end= c(2017,4), frequency= 4)

@@

```{r}
reg_kuld_start=dynlm(TSDELTALOG(kuld_2017) ~ 1 + L(TSDELTALOG(kuld_2017),1:4) +  L(TSDELTALOG(komp_r_obs1_2017),0:4)+ L(log(kuld_2017),1) + L(log(komp_r_obs1_2017),1)+ d_2013q1)

@@

```{r}
checkresiduals(res_reg_kuld)
```

@@

 kuld_vars_1 <- str_c("L(TSDELTALOG(kuld_2017), 1:4)", c(1,2,3,4))
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs1_2017), 0:4)", c(1,2,3))

@@

```{r}
reg_kuld=dynlm(TSDELTALOG(kuld_2017) ~ 0 +L(log(kuld_2017),1) + L(log(komp_r_obs1_2017),1)+ d_2013q1 )

summary(reg_kuld)
```
```{r}
res_reg_kuld_done=residuals(reg_kuld)
shapiro.test(res_reg_kuld_done)
```
